--- 
title: "我的个人日记"
author: "王超辰"
date: "始于2016年6月21日"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: "apalike"
link-citations: true
github-repo: winterwang/personal_book
description: "你正在阅读我的日记，我的想法，我的心路历程。"
knit: "bookdown::render_book"
output: 
  bookdown::gitbook:
    lib_dir: "book_assets"
  bookdown::pdfbook:
    keep_tex: yes
---

# 把bookdown也当作一种记录方式

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
